\documentclass[10pt]{article}
\usepackage{geometry}
\geometry{margin=2cm}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{longtable}
\usepackage{setspace}
\usepackage{tcolorbox}  % for color boxes
\usepackage{booktabs}

% Font settings
\setmainfont{Merriweather}
\newfontface\sectionfont{Merriweather}

\title{\textbf{Semper Fidelis Group Book Review Rota and Guidelines}}
\date{}

\begin{document}

\maketitle

\section*{Introduction}
The Semper Fidelis group book review aims to foster a collaborative and enriching environment where members can engage deeply with selected literature. Through structured discussions and shared insights, the group seeks to enhance understanding, encourage diverse perspectives, and build a strong community of avid readers.

\section*{Guidelines}

\subsection*{Time Allocation}
\begin{itemize}
    \item \textbf{Presenter:} 45 minutes
    \item \textbf{Moderator:} 10 minutes (to call the meeting to order, ensuring everyone arrives on time)
    \item \textbf{Timekeeper:} Ongoing throughout the session
    \item \textbf{Note-taker:} Ongoing throughout the session
    \item \textbf{Discussion:} 30 minutes
\end{itemize}

\subsection*{Submission Deadlines}
\begin{itemize}
    \item Individual summaries or notes must be submitted 48 hours before the scheduled presentation to ensure timely preparation and distribution.
\end{itemize}

\subsection*{Etiquette During Discussions}
\begin{itemize}
    \item Be respectful and attentive when others are speaking.
    \item Encourage participation from all members.
    \item Keep discussions focused on the book and related topics.
    \item Avoid interrupting others and allow everyone to express their thoughts.
\end{itemize}

\subsection*{Role Descriptions}
\begin{itemize}
    \item \textbf{Moderator:} Facilitates the discussion, ensures the session stays on topic, and manages the overall flow of the meeting.
    \item \textbf{Presenter:} Delivers a summary and analysis of the assigned book or chapter, highlighting key points and insights.
    \item \textbf{Timekeeper:} Monitors the time allocated for each section of the meeting and provides reminders to keep the session on schedule.
    \item \textbf{Note-taker:} Records key points, insights, and action items from the discussion and distributes the notes to all members promptly.
\end{itemize}

\section*{Rota Table}

% Line spacing
\onehalfspacing

% Header and footer settings
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{Semper Fidelis Group Book Review}} 
\fancyhead[R]{\thepage}

% Color definitions
\definecolor{darkgreen}{RGB}{0,100,0}
\definecolor{blue}{RGB}{0,0,255}
\definecolor{purple}{RGB}{128,0,128}
\definecolor{navyblue}{RGB}{0,0,128}
\definecolor{maroon}{RGB}{128,0,0}
\definecolor{teal}{RGB}{0,128,128}

% Custom commands for colored names
\newcommand{\authorname}[1]{\textcolor{darkgreen}{#1}}
\newcommand{\reviewername}[1]{\textcolor{purple}{#1}}

% Hyperlink settings
\hypersetup{
    colorlinks=true,
    linkcolor=navyblue,
    urlcolor=teal,
}

% Start color box for the table
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|@{}p{2.5cm}|@{}p{2.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Week/Date} & \textbf{Book/Chapter} & \textbf{Presenter} & \textbf{Moderator} & \textbf{Timekeeper} & \textbf{Note-taker} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Week 1: Feb 2, 2025} & \textbf{Chapter 8: Stewardship} & \authorname{BOSIBORI} & \reviewername{ROSE} & \authorname{MAGOMA} & \authorname{MOSETA} \\
\hline
\textbf{Week 2: Feb 9, 2025} & \textbf{Chapter 9: Fasting} & \authorname{MAKANA} & \reviewername{BOSIBORI} & \reviewername{JEROP} & \authorname{ANITA} \\
\hline
\textbf{Week 3: Feb 16, 2025} & \textbf{Chapter 10: Silence and Solitude} & \authorname{MOSETA} & \authorname{MAKANA} & \authorname{BOSIBORI} & \reviewername{JEROP} \\
\hline
\textbf{Week 4: Feb 23, 2025} & \textbf{Chapter 11: Journaling} & \authorname{MAGOMA} & \authorname{ANITA} & \reviewername{ROSE} & \authorname{BOSIBORI} \\
\hline
\textbf{Week 5: Mar 2, 2025} & \textbf{Chapter 12: Learning} & \authorname{ANITA} & \authorname{MOSETA} & \authorname{MAKANA} & \authorname{MAGOMA} \\
\hline
\textbf{Week 6: Mar 9, 2025} & \textbf{Chapter 13: Perseverance in the Disciplines} & \reviewername{ROSE} & \reviewername{BOSIBORI} & \reviewername{JEROP} & \authorname{MOSETA} \\
\hline
\end{longtable}
\end{tcolorbox}

\section*{Meeting Agenda}
\begin{enumerate}
    \item \textbf{Opening Prayer} (5 mins) - MOD\\
    Begin with a brief prayer to set the tone for the session.
    
    \item \textbf{Review of Previous Session} (10 mins) - Previous Pr
    \begin{itemize}
        \item Recap key points from the last meeting.
        \item Discuss any follow-up items.
    \end{itemize}
    
    \item \textbf{Main Teaching/Discussion} (45 mins) - Pr
    \begin{itemize}
        \item Dive into the assigned book/chapter.
        \item Led by the designated presenter.
        \item Encourage active participation and questions.
    \end{itemize}
    
    \item \textbf{Personal Application Sharing/Discussion} (30 mins) - NT
    \begin{itemize}
        \item Members share personal insights or how the reading applies to their lives.
        \item Open floor for reflections.
    \end{itemize}
    
    \item \textbf{Prayer Requests and Closing} (10 mins) - MOD
    \begin{itemize}
        \item Share prayer needs within the group.
        \item Close with a group prayer.
    \end{itemize}
\end{enumerate}

\textbf{Abbreviations:} MOD - Moderator; Previous Pr - Previous Presenter; NT - Note-taker

\section*{Additional Notes}
\begin{itemize}
    \item \textbf{Holiday Break:} There will be a break from December 16-29, 2024.
    \item \textbf{Meeting Times:}
    \begin{itemize}
        \item \textbf{Thursdays:} 8:30-10:00 PM
        \item \textbf{Sundays:} 11:00 AM-1:30 PM (longer sessions)
    \end{itemize}
    \item Please ensure all roles are aware of their responsibilities before each meeting.
    \item If unable to attend or fulfill a role, notify the group at least 24 hours in advance.
    \item Maintain punctuality to respect everyone's time and the structure of the meeting.
    \item Encourage an open and inclusive atmosphere where all members feel comfortable sharing their thoughts.
\end{itemize}

\newpage
\section*{Role Assignments}
Here is a **specialized table for each person** showing their roles and the dates they are assigned to those roles:

---

\subsection*{Anita}
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Date} & \textbf{Chapter} & \textbf{Role} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Feb 9, 2025} & \textbf{Chapter 9: Fasting} & \textbf{Note-taker} \\
\hline
\textbf{Feb 23, 2025} & \textbf{Chapter 11: Journaling} & \textbf{Moderator} \\
\hline
\textbf{Mar 2, 2025} & \textbf{Chapter 12: Learning} & \textbf{Presenter} \\
\hline
\end{longtable}
\end{tcolorbox}

---

\subsection*{Magoma}
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Date} & \textbf{Chapter} & \textbf{Role} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Feb 2, 2025} & \textbf{Chapter 8: Stewardship} & \textbf{Timekeeper} \\
\hline
\textbf{Feb 23, 2025} & \textbf{Chapter 11: Journaling} & \textbf{Presenter} \\
\hline
\textbf{Mar 2, 2025} & \textbf{Chapter 12: Learning} & \textbf{Note-taker} \\
\hline
\end{longtable}
\end{tcolorbox}

---

\subsection*{Rose}
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Date} & \textbf{Chapter} & \textbf{Role} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Feb 2, 2025} & \textbf{Chapter 8: Stewardship} & \textbf{Moderator} \\
\hline
\textbf{Feb 23, 2025} & \textbf{Chapter 11: Journaling} & \textbf{Timekeeper} \\
\hline
\textbf{Mar 9, 2025} & \textbf{Chapter 13: Perseverance in the Disciplines} & \textbf{Presenter} \\
\hline
\end{longtable}
\end{tcolorbox}

---

\subsection*{Jerop}
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Date} & \textbf{Chapter} & \textbf{Role} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Feb 9, 2025} & \textbf{Chapter 9: Fasting} & \textbf{Timekeeper} \\
\hline
\textbf{Feb 16, 2025} & \textbf{Chapter 10: Silence and Solitude} & \textbf{Note-taker} \\
\hline
\textbf{Mar 9, 2025} & \textbf{Chapter 13: Perseverance in the Disciplines} & \textbf{Timekeeper} \\
\hline
\end{longtable}
\end{tcolorbox}

---

\subsection*{Bosibori}
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Date} & \textbf{Chapter} & \textbf{Role} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Feb 2, 2025} & \textbf{Chapter 8: Stewardship} & \textbf{Presenter} \\
\hline
\textbf{Feb 9, 2025} & \textbf{Chapter 9: Fasting} & \textbf{Moderator} \\
\hline
\textbf{Feb 16, 2025} & \textbf{Chapter 10: Silence and Solitude} & \textbf{Timekeeper} \\
\hline
\textbf{Feb 23, 2025} & \textbf{Chapter 11: Journaling} & \textbf{Note-taker} \\
\hline
\textbf{Mar 9, 2025} & \textbf{Chapter 13: Perseverance in the Disciplines} & \textbf{Moderator} \\
\hline
\end{longtable}
\end{tcolorbox}

---

\subsection*{Moseta}
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Date} & \textbf{Chapter} & \textbf{Role} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Feb 2, 2025} & \textbf{Chapter 8: Stewardship} & \textbf{Note-taker} \\
\hline
\textbf{Feb 16, 2025} & \textbf{Chapter 10: Silence and Solitude} & \textbf{Presenter} \\
\hline
\textbf{Mar 2, 2025} & \textbf{Chapter 12: Learning} & \textbf{Moderator} \\
\hline
\textbf{Mar 9, 2025} & \textbf{Chapter 13: Perseverance in the Disciplines} & \textbf{Note-taker} \\
\hline
\end{longtable}
\end{tcolorbox}

---

\subsection*{Makana}
\begin{tcolorbox}[colframe=blue!40, colback=yellow!10, coltitle=black, sharp corners=south, boxrule=0.4mm, width=\textwidth-2mm]
\renewcommand{\arraystretch}{1.5} % Increase row height
\begin{longtable}{|@{}p{2.5cm}|@{}p{3.5cm}|@{}p{2.5cm}|}
\hline
\textbf{Date} & \textbf{Chapter} & \textbf{Role} \\
\hline
\endhead
\hline
\endlastfoot
\textbf{Feb 9, 2025} & \textbf{Chapter 9: Fasting} & \textbf{Presenter} \\
\hline
\textbf{Feb 16, 2025} & \textbf{Chapter 10: Silence and Solitude} & \textbf{Moderator} \\
\hline
\textbf{Mar 2, 2025} & \textbf{Chapter 12: Learning} & \textbf{Timekeeper} \\
\hline
\end{longtable}
\end{tcolorbox}

\end{document}